---
title: "MDPyramid"
output: github_document
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## MDPyramid Doc

Simple MDPyramid script in R. 
Delivers 2 possible routes with maximum sums.

The task to find the maximum sum of the numbers per the given rules below:  

1. You will start from the top and move downwards to an adjacent number as in below.  
2. You are only allowed to walk downwards and diagonally.  
3. You should walk over the numbers as evens and odds subsequently. Suppose that you are on an even number the next number you walk must be odd, or if you are stepping over an odd number the next number must be even. In other words, the final path would be like Odd -> even -> odd -> even …  
4. You must reach to the bottom of the pyramid.  

The goal is to find the maximum sum if you walk the path. 

* This is v02

## Code

R code in the document as follows:

```{r warning=FALSE}
pacman::p_load(tidyverse, data.table, stringr, magrittr,glue)

file <- "https://raw.githubusercontent.com/vinciuna/MDPyramid/master/binaryTree_test.txt"
dt <- readLines(con = file)
dt
max <- dt %>% map_int(.,~str_count(.,"\\s+")) %>% max()
dt %<>% map_chr(., ~str_c(., str_c(rep(" 0",max-str_count(.,"\\s")),collapse = ""),sep=""))
dt <- str_split(dt,"\\s")
dt <- pmap_dfc(dt,rbind) %>% mutate_all(.,as.integer)
```

Functions:

```{r functions}
dt_clean <- function(x,p) {
  if (p==1){
    x[!(seq(x)%%2 == x%%2)] <- 0} else
    {x[(seq(x)%%2 == x%%2)] <- 0}
  x[x==0] <- -Inf
  x
}
#binary tree elements grouping
split2 <- function(v, seg.length, seg.over) {
  if (length(v)< seg.length){return(v) }
  else{
    starts = seq(1, length(v)-1, by=seg.length-seg.over)
    ends = starts + seg.length - 1
    ends[ends > length(v)] = length(v)
    lapply(1:length(starts), function(i) v[starts[i]:ends[i]])
  }
}
#summing vectors
fadd <- function(v1,v2){
  sums=v1+v2
  max=max(sums)
  maxid=which(sums==max)
  adds=list(v1[v1!=-Inf], v2[v2!=-Inf])
  if (max!=-Inf){
    list(max=max,
         maxid=maxid,
         sums=sums[sums!=-Inf],
         adds=adds)
  } else return(-Inf)
}
#as.integer customized
as.integer0 <- function(x)
{
  x <- as.integer(x)
  if (length(x)==0 ) x=-Inf
  else x=x
  x
}
```
Data setup:
* cleaning table with impossible 
```{r data setup}
#data setup
par <- dt[[1,1]]%%2
dt %<>%  mutate_all(~dt_clean(.,par))
dt
n <- nrow(dt)
x2 <- dt[n,] %>% as.numeric(.)
lc <- seq(n)
path <- as.list(lc);p_<- NULL

```
Looping over nodes:
```{r loop}
#loop over nodes
for (i in (n-1):1 ) {
  x2 %<>% split2(.,2,1)
  lc %<>% split2(.,2,1)
  x1 <- dt[i,] %>% as.numeric(.)
  path[[i]] <- as.list(x=1:length(x2))
  for (j in 1:length(x2) ){
    add_ <- fadd(x1[j],x2[[j]])
    if (is.list(add_)) {
      lc[[j]] <- j+add_$maxid-1
      path[[i]][[j]] <- list(set_=j,
                             nodes_= c(x2[[j]][[add_$maxid]],x1[j]),
                             sum_=add_$max )
      x2[[j]] <- add_$max
    } else {
      lc[[j]] <- -Inf
      x2[[j]] <- -Inf
    }
  }
  x2 %<>% unlist()
}
```
#Rezults:
```{r rezults}
cat("sum=",path[[1]][[1]]$sum_,"\n")
sum.l <- path[[1]][[1]]$nodes_[1]
p_[1] <- path[[1]][[1]]$nodes_[2]
for (i in 2:(n-1) ) {
  sums <- map(path[[i]],"sum_") %>% map(as.integer0) %>% unlist()
  j <- which(sums==sum.l)
  p_[i] <- map(path[[i]],"nodes_") %>% .[[j]] %>% .[2]
  #cat(p_,"+")
  sum.l <- path[[i]][[j]]$nodes_[1]
}
p_[n] <- map(path[[i]],'nodes_') %>% .[[j]] %>% .[1]
glue("path: {paste0(p_,collapse = ' + ')}")

```

```{r}

```
